KidsAIR: manuscript tables/figures

### 2021-09-07 main_analysis_final.Rmd
Annotate/organize code for main outcomes paper

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 9 June 2021"
output: pdf_document
---

@@

analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         pm_mean_at_home_sampling_period = pm_at_home_sampling_period,
         lrti_events_di_total = as.factor(lrti_events_di_total),
         person_time_at_risk_iqr = person_time_at_risk/20,
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) 
  #filter(area == "WMT")
  #filter(gender == "Female")
  #filter(home_sqft_2level == "1500+")

analysis_data_outliers <- analysis_data %>% 
  #rownames_to_column() %>% 
  #mutate(filter_outliers = if_else(rowname %in% c(57), 1, 0)) %>% 
  mutate(log_person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 2.33, log_person_time_at_risk)) %>% 
  mutate(person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 72, person_time_at_risk),
         lrti_events_total = as.factor(lrti_events_total),
         lrti_events_di_total = as.factor(lrti_events_di_total),
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")))

analysis_data_winter1 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         pm_mean_at_home_sampling_period = pm_at_home_sampling_period,
         lrti_events_di_winter = as.factor(lrti_events_di_winter),
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) %>% 
  #filter(person_time_at_risk_winter > 0) %>% 
  #filter(area == "WMT") %>% 
  filter(winter_id == 1)

analysis_data_winter2 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         pm_mean_at_home_sampling_period = pm_at_home_sampling_period,
         lrti_events_di_winter = as.factor(lrti_events_di_winter),
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  filter(winter_id == 2)

analysis_data_noak <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         pm_mean_at_home_sampling_period = pm_at_home_sampling_period,
         lrti_events_di_total = as.factor(lrti_events_di_total),
         person_time_at_risk_iqr = person_time_at_risk/20,
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) %>% 
  filter(area != "AK")
```

@@

int_function(analysis_data, "residents_smoke")
n_table
save_contrasts
pm_summary_table
lrti_summary_table
save_summary
save_contrasts_full

@@

```{r, eval=FALSE, include=FALSE}
# Run and save model results

@@

int_function(winter_1_data_pm, "stove_grade_3level")

@@

((exp(-0.07214)-1)*100)
```

```{r, eval=FALSE, include=FALSE} 
# Run and save model results

@@

## Model summary and diagnostic plots
```{r}
summary(er_results)
er_res <- simulateResiduals(er_results)
testDispersion(er_res, alternative = "two.sided")
plot(er_res, rank = TRUE, quantreg = TRUE)
```

@@

int_function(analysis_data, "residents_smoke")
save_contrasts
pm_summary_table
lrti_summary_table
save_summary

@@

@@

```{r, eval=FALSE, include=FALSE}
################ Plot/check individual models and various results ##############

>>>>

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 7 September 2021"
output: pdf_document
---

@@

# Primary analysis dataset - load and format a few variables
analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         pm_mean_at_home_sampling_period = pm_at_home_sampling_period,
         lrti_events_di_total = as.factor(lrti_events_di_total),
         person_time_at_risk_iqr = person_time_at_risk/20,
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know"))
  #filter(!is.na(home_sqft_2level))
  #filter(area == "WMT")
  #filter(gender == "Female")
  #filter(home_sqft_2level == "1500+")

# Dataset for sensitivity analysis - replace "outlier" for person time with mean value
analysis_data_outliers <- analysis_data %>% 
  #rownames_to_column() %>% 
  #mutate(filter_outliers = if_else(rowname %in% c(57), 1, 0)) %>% 
  mutate(log_person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 2.33, log_person_time_at_risk)) %>% 
  mutate(person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 72, person_time_at_risk),
         lrti_events_total = as.factor(lrti_events_total),
         lrti_events_di_total = as.factor(lrti_events_di_total),
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")))

# Dataset for sensitivity analysis - filter for Winter 1 data only
analysis_data_winter1 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         pm_mean_at_home_sampling_period = pm_at_home_sampling_period,
         lrti_events_di_winter = as.factor(lrti_events_di_winter),
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) %>% 
  #filter(person_time_at_risk_winter > 0) %>% 
  #filter(area == "WMT") %>% 
  filter(winter_id == 1)

# Dataset for sensitivity analysis - filter for Winter 2 data only
analysis_data_winter2 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         pm_mean_at_home_sampling_period = pm_at_home_sampling_period,
         lrti_events_di_winter = as.factor(lrti_events_di_winter),
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  filter(winter_id == 2)

# Dataset for sensitivity analysis - filter out AK data
analysis_data_noak <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_mean_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         pm_mean_at_home_sampling_period = pm_at_home_sampling_period,
         lrti_events_di_total = as.factor(lrti_events_di_total),
         person_time_at_risk_iqr = person_time_at_risk/20,
         child_age = factor(child_age, levels = c("< 1", "1+")),
         moisture_di = cut(moisture_closest, breaks = c(0, 11, 100),
                           labels = c("<11%", ">=11%")),
         stove_age_di = fct_collapse(stove_age_3level, 
                                     "0-5 years old" = "0-5 years old",
                                     "6+ years old" = c("6-15 years old", "16 + years old"),
                                     "Do not know" = "Do not know")) %>% 
  filter(area != "AK")
```

@@

# Run function with selected interaction term
# Use next few lines to help fill in Tables for publication
int_function(analysis_data, "residents_smoke")

@@

```{r, eval=FALSE, include=FALSE} 
# Run and save model results for various sensitivity analyses

@@

# Run function with selected interaction term
# Use next few lines to help fill in Tables for publication
int_function(winter_1_data_pm, "stove_grade_3level")

@@

((exp(-0.07214)-1)*100) # formula for exponentiating results (percent difference)
```

```{r, eval=FALSE, include=FALSE} 
# Run and save model results for various sensitivity analyses

@@

## Model summary and diagnostic plots
```{r}
summary(er_results)
#summary(er_results2)
er_res <- simulateResiduals(er_results)
testDispersion(er_res, alternative = "two.sided")
plot(er_res, rank = TRUE, quantreg = TRUE)
```

@@

# Run function with selected interaction term
# Use next few lines to help fill in Tables for publication
int_function(analysis_data, "residents_smoke")
save_contrasts
pm_summary_table
lrti_summary_table
save_summary

@@

nobs(er_stove_age_results)

@@

```{r, eval=FALSE, include=FALSE}
################ Code to plot/check individual models and various results ##############

### 2021-09-07 manuscript_tables_figures.Rmd
Annotate/organize code for main outcomes paper

---
title: 'KidsAIR: manuscript tables/figures'
author: "Ethan Walker"
date: "Started 13 May 2020, Updated 30 June 2020"
output:
  powerpoint_presentation: default
---

@@

```{r}
demographics_summary <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 | winter_id == 0) %>% 
  arrange(winter_id) %>% 
  #filter(treatment_assigned == "Placebo") %>%
  distinct(child_id_char, .keep_all = TRUE)

@@

```{r}
# summary data for manuscript tables
num_funct_total <- function(var, data = health_exposure_data_sampling_day){

@@

```{r}
other_vars_total <- health_exposure_data_sampling_day %>% 
  rename(new_var = home_act_sweep_sum) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment_assigned == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
other_vars_total

>>>>

---
title: 'KidsAIR: manuscript tables/figures'
author: "Ethan Walker"
date: "Started 13 May 2020, Updated 7 September 2021"
output:
  powerpoint_presentation: default
---

@@

# Character/factor data summary stats
```{r}
demographics_summary <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 | winter_id == 0) %>% 
  arrange(winter_id) %>% 
  #filter(treatment_assigned == "Placebo") %>%
  distinct(child_id_char, .keep_all = TRUE)

@@

# Numeric data summary stats
```{r}
# summary data for manuscript tables
num_funct_total <- function(var, data = health_exposure_data_sampling_day){

@@

# Summarize home activity variables
```{r}
other_vars_total <- health_exposure_data_sampling_day %>% 
  rename(new_var = home_act_sweep_sum) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment_assigned == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
other_vars_total
